 

### 2021-06-12 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

In the face of global climate change, certain forests, such as African rainforests [Amy Bennett's new paper] are more resilient to warming and drought than other temperate and tropical forests. Additionally, increasing temperature acclimation among tropical and boreal species [martijn's papers; Danielle Way's papers; Atkin's papers] and reversible recovery of canopy heat stress [Smith et al. 2020] among other mechanisms [for eg. *REF*], point towards rays of hope.

>>>>

In the face of global climate change, resiliency among forests are also observed, such as African rainforests [Amy Bennett's new paper] that are more resilient to warming and drought than other forests. Increasing temperature acclimation among tropical and boreal species [martijn's papers; Danielle Way's papers; Atkin's papers] and reversible recovery of canopy heat stress [Smith et al. 2020] are other mechanisms [for eg. *REF*] that will help cope with warming.
